---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
#Load the data
```{r loaddata}
library(data.table)
DT <- data.table(read.csv("activity.csv"))
```


## What is mean total number of steps taken per day?
```{r}
library(ggplot2)
total.steps <- tapply(DT$steps, DT$date, FUN=sum, na.rm=TRUE)
#histogram of the total number of steps taken each day
qplot(total.steps, binwidth=3, xlab="total number of steps taken each day", main="Fig 1")+ geom_histogram(colour="steelblue4", fill="steelblue4")
#mean total number of steps taken per day
mean(total.steps, na.rm=TRUE)
#median total number of steps taken per da
median(total.steps, na.rm=TRUE)
```
Average (Mean) number of steps per day is **9354.23**

The median number of steps per day is **10,395**


## What is the average daily activity pattern?
Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days

```{r}
library(ggplot2)
averages <- aggregate(x=list(steps=DT$steps), by=list(interval=DT$interval), FUN=mean, na.rm=TRUE)
ggplot(data=averages, aes(x=interval, y=steps)) +geom_line(color = "steelblue4", lwd = 2) + xlab("5-minute interval") + ylab("average number of steps taken")+ labs(title = expression("Fig 2"))
```

On average across all the days in the dataset, the 5-minute interval contains
the maximum number of steps?
```{r}
averages[which.max(averages$steps),]
```

The 5-minute interval that contains the maximum averaged number of steps is 8:35 am (**835**).  The maximum averaged number of steps is **206.1698**


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
